Software Citation Principles

### 2016-03-07 sc-principles/software-citation-principles.tex
reformatted use case table with vertical column headers; added license, evaluator use case

\usepackage[table]{xcolor}
\usepackage{dcolumn}
\usepackage{float}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{subfigure}
\usepackage{psfrag}
\usepackage{tabularx}
\usepackage[hyphens]{url}
\usepackage{wrapfig}
\usepackage{longtable}
\usepackage{verbatim}
\usepackage{booktabs,multicol}

@@

We have documented and analyzed a set of use cases related to software citation in \cite{SC-Use-Cases}.
Table~\ref{tab:use_cases} summarizes these use cases and makes clear what the requirements are for software citation in each case.
\katznote{not sure if this next long sentence should be here, should be in the table caption, or should be footnotes to the table, or even more than one of these}
\niemnote{Not sure either; definitely should include in the text due to length. Maybe an abbreviated version in the caption?}\flnote{If these ``definitions'' are not used anywhere else than in the table (and they don't really seem to be so far), then I tend towards putting this in the caption. That's where they are needed (in the table). I don't like footnotes for something like this.}\dmnote{Agree it would be better in the caption.}
In the table,
``researcher'' includes both academic researchers (e.g., postdoc, tenure-track faculty member) and research software engineers;
``publisher'' includes both traditional publishers that publish text and\slash or software papers as well as archives such as Zenodo that directly publish software;
``reproduce'' can mean reproduction, replication, verification, validation, repeatability, and\slash or utility;
examples of indexers include Scopus, Web of Science, Google Scholar, and Microsoft Academic Search;
domain groups include bioCADDIE, CIG, etc.;\dmnote{Not sure what CIG stands for, and acronyms should probably be explained or linked}
``repository'' refers to public software repositories such as ASCL,
GitHub, Netlib, CRAN, institutional repositories;
``funder'' is a group that funds software or work using software; and
``UID'' means unique ID, such as a DOI or PURL.

\rowcolors{5}{white}{gray!25}
\begin{table}[htbp]
\caption{Use cases for software citation, adapted from \cite{SC-Use-Cases} \flnote{Also, I noticed that some entries have the same requirements: maybe they could be combined to one line?} \dmnote{I would leave them separate. What about adding a column for license?}}
\centering
\scriptsize\setlength{\tabcolsep}{2.5pt}
\begin{tabular}{@{}l l c c c c c c c c@{}}
\toprule
 & & \multicolumn{6}{c}{Requirements} \\
 \cmidrule{3-10}
\multirow{2}{*}{Stakeholder} &	\multirow{2}{*}{Use\slash wants to} 	 &  Software  & \multirow{2}{*}{Author(s)} & \multirow{2}{*}{Version \#} & Release & Location\slash  & \multirow{2}{*}{UID} & Indexed & \multirow{2}{*}{Role} \\
& & name &  &  &  date & repository &  & citations & \\
\midrule
Researcher            & use someone else's software for a paper      & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             &             \\
Researcher            & use someone else's software for new software & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             &             \\
Researcher            & contribute to software                   & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             & \textbullet \\
Researcher            & find citations of software               & \textbullet &             &             &             &             & \textbullet & \textbullet &             \\
Researcher            & get credit for software development          & \textbullet & \textbullet &             & \textbullet & \textbullet & \textbullet &             & \textbullet \\
Researcher            & ``reproduce'' analysis                   & \textbullet &             & \textbullet & \textbullet & \textbullet & \textbullet &             &             \\
Researcher            & benchmark software                       & \textbullet &             & \textbullet & \textbullet & \textbullet & \textbullet &             &             \\
Researcher            & find software to implement task          & \textbullet & \textbullet &             &             & \textbullet & \textbullet & \textbullet &             \\
Publisher             & publish software paper                   & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             &             \\
Publisher             & publish papers that cite software        & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             \\
Indexer               & build catalog of software                & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             \\
Domain group          & build catalog of software                & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             &             \\
Library\slash archive & build catalog of software                & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             &             \\
Repository            & show scientific impact of holdings       & \textbullet &             &             &             &             & \textbullet & \textbullet &             \\
Funder                & show how funded software has been used   & \textbullet &             &             &             &             & \textbullet & \textbullet &             \\
\bottomrule
\end{tabular}
\label{tab:use_cases}
\end{table}%

>>>>

\usepackage[table]{xcolor}
\usepackage{dcolumn}
\usepackage{float}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{subfigure}
\usepackage{psfrag}
\usepackage{tabularx}
\usepackage[hyphens]{url}
\usepackage{wrapfig}
\usepackage{longtable}
\usepackage{verbatim}
\usepackage{booktabs,multicol}
\usepackage{rotating}

@@

We have documented and analyzed a set of use cases related to software citation in \cite{SC-Use-Cases}.
Table~\ref{tab:use_cases} summarizes these use cases and makes clear what the requirements are for software citation in each case.
\katznote{not sure if this next long sentence should be here, should be in the table caption, or should be footnotes to the table, or even more than one of these}
\niemnote{Not sure either; definitely should include in the text due to length. Maybe an abbreviated version in the caption?}\flnote{If these ``definitions'' are not used anywhere else than in the table (and they don't really seem to be so far), then I tend towards putting this in the caption. That's where they are needed (in the table). I don't like footnotes for something like this.}\dmnote{Agree it would be better in the caption.}
In the table,
``researcher'' includes both academic researchers (e.g., postdoc, tenure-track faculty member) and research software engineers;
``publisher'' includes both traditional publishers that publish text and\slash or software papers as well as archives such as Zenodo that directly publish software;
``reproduce'' can mean reproduction, replication, verification, validation, repeatability, and\slash or utility;
examples of indexers include Scopus, Web of Science, Google Scholar, and Microsoft Academic Search;
domain groups include bioCADDIE, CIG, etc.;\dmnote{Not sure what CIG stands for, and acronyms should probably be explained or linked}
``repository'' refers to public software repositories such as ASCL,
GitHub, Netlib, CRAN, institutional repositories;
``funder'' is a group that funds software or work using software; and
``unique ID'' refers to identifiers such as a DOI or PURL.

%
\newcommand*\rot[1]{\begin{turn}{90} #1 \end{turn}}%
\rowcolors{4}{gray!25}{white}
\begin{table}[htbp]
\caption{Use cases for software citation, adapted from \cite{SC-Use-Cases}}
\centering
\scriptsize\setlength{\tabcolsep}{2.5pt}
\begin{tabular}{@{}l l c c c c c c c c c@{}}
\toprule
 & & \multicolumn{7}{c}{Requirements} \\
 \cmidrule{3-11}
Stakeholder & Use\slash wants to 	&  \rot{Software name} & \rot{Author(s)} & \rot{Version number} & \rot{Release date} & \rot{Location\slash repository} & \rot{Unique identifier} & \rot{Indexed citations} & \rot{Contributor role} & \rot{Software license}  \\
\midrule
Researcher            & use someone else's software for a paper      & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             &             & \textbullet \\
Researcher            & use someone else's software for new software & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             &             & \textbullet \\
Researcher            & contribute to software                   & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet\\
Researcher            & find citations of software               & \textbullet &             &             &             &             & \textbullet & \textbullet &            & \\
Researcher            & get credit for software development          & \textbullet & \textbullet &             & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet  \\
Researcher            & ``reproduce'' analysis                   & \textbullet &             & \textbullet & \textbullet & \textbullet & \textbullet &             &            & \textbullet \\
Researcher            & benchmark software                       & \textbullet &             & \textbullet & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet \\
Researcher            & find software to implement task          & \textbullet & \textbullet &             &             & \textbullet & \textbullet & \textbullet &             & \textbullet \\
Publisher                  & publish software paper                   & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             &             & \\
Publisher                  & publish papers that cite software        & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             & \\
Indexer                     & build catalog of software                & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet \\
Domain group           & build catalog of software                & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet \\
Library\slash archive & build catalog of software                & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet \\
Repository                 & show scientific impact of holdings       & \textbullet &             &             &             &             & \textbullet & \textbullet &             &             \\
Funder                       & show how funded software has been used   & \textbullet &             &             &             &             & \textbullet & \textbullet &             &             \\
Evaluator                   & evaluate contributions of researcher   &                  & \textbullet &             & \textbullet &             & \textbullet & \textbullet & \textbullet &             \\
\bottomrule
\end{tabular}
\label{tab:use_cases}
\end{table}%
